\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xparse}
\input{glyphtounicode}

\usepackage{ulem}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\bfseries\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------------------------

\newcommand{\resumeItem}[1]{
\item\small{
    {#1 \vspace{-2pt}}
  }
}

\NewDocumentCommand\resumeSubheading{mmmmo}{
  \vspace{-2pt}
\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#4\IfNoValueTF{#5}{}{ $|$ #5}} & \textit{\small #3} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{
\end{itemize}}
\newcommand{\resumeItemListStart}{
\begin{itemize}}
    \newcommand{\resumeItemListEnd}{
\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

\begin{center}
  \textbf{\Huge Chakorn Kungsanarux} \\ \vspace{0.35cm}

  \href{mailto:chakornk2007@gmail.com}{\uline{chakornk2007@gmail.com}}%
  \kern 0.5 cm%
  \href{https://www.linkedin.com/in/chakorn-kungsanarux}{\uline{linkedin.com/in/chakorn-kungsanarux}}%
  \kern 0.5 cm%
  \href{https://github.com/chakornk}{\uline{github.com/chakornk}}%
  \kern 0.5 cm%
  \href{https://chakornk.dev}{\uline{chakornk.dev}}%
\end{center}

%-------------------------------------------

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of British Columbia}{2025 - 2029 (expected)}
{Bachelor of Science}{Vancouver, BC}
\resumeSubHeadingListEnd

%-------------------------------------------

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Motion UBC}{Nov. 2025 - Present}{Vancouver, BC}
{Developer}[TypeScript, PHP, Lavarel, React, Tailwind]
\resumeItemListStart
\resumeItem{Worked on a pro-bono software project for processing, storing, and managing client information.}
\resumeItem{Designed and created frontend UI for authentication pages.}
\resumeItemListEnd

\resumeSubheading
{Google Developers Student Club UBC}{Sep. 2025 - Present}{Vancouver, BC}
{Product Developer}[TypeScript, Next.js, React, Tailwind, AWS S3, Prisma]
\resumeItemListStart
\resumeItem{Created a web app for tracking and predicting disease outbreaks.}
\resumeItem{Reduced load time of a web app used in an event with 40+ participants by 75\%.}
\resumeItemListEnd

\resumeSubheading
{Learning Buddies Network}{Oct. 2023 - May 2024}{Vancouver, BC}
{Math Mentor}
\resumeItemListStart
\resumeItem{Tutored elementary school students in weekly one-on-one sessions.}
\resumeItem{Prepared lessons ahead of time to better fit with a student's knowledge of various math topics.}
\resumeItem{Received the "Outstanding Mentor" award in June 2024.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------

\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{Equation Visualizer}{2025}
{Vue.js, WebGL}
\resumeItemListStart
\resumeItem{Created a web app that allows users to enter a mathematical equation and view its heatmap.}
\resumeItemListEnd

\resumeProjectHeading
{MasterMath}{2025}
{Next.js, React, Tailwind, MongoDB, Google OAuth}
\resumeItemListStart
\resumeItem{Developed a web app for helping high school students practice math in a more engaging way through a reward system.}
\resumeItem{Implemented JWT to authorize requests.}
\resumeItemListEnd

\resumeProjectHeading
{Club Manager}{2025}
{Next.js, React, Tailwind}
\resumeItemListStart
\resumeItem{Developed a web app for managing high school clubs that allows users to create, modify, and join clubs digitally.}
\resumeItem{Designed and implemented REST APIs to integrate frontend and backend.}
\resumeItemListEnd

\resumeProjectHeading
{JH Eagles}{2024}
{Flutter, GitHub Actions}
\resumeItemListStart
\resumeItem{Built a mobile app based on Material Design 3 that displays school-related information, taking data from the official school app's API.}
\resumeItem{Used GitHub Actions to automate building app and pushing new updates.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{
        \textbf{Languages}{: TypeScript, HTML/CSS, PHP, Dart, Python, GLSL, R} \\
        \textbf{Frameworks}{: Next.js, React, Vue.js, Express.js, React Native, Electron.js, Flutter} \\
        \textbf{Libraries}{: Tailwind CSS, PixiJS, Mongoose} \\
        \textbf{Developer Tools}{: Git, GitHub Actions, Docker, Figma, VS Code} \\
    }}
\end{itemize}

\end{document}
